A Survey Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
wrote data type section.

\subsection{Question Format}
In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]

@@

%SE: This doesn't add much, the numbers can be put in the text to save space.
%\begin{figure}
%	\centering
%	\includegraphics[width=0.5\textwidth]{recipient.png}
%	\caption{(This is a placeholder! TODO: generate a better plot for data recipient)}
%\end{figure}

@@

\subsubsection{Data Type}
INTRO HERE.

@@

TALK ABOUT WHAT WAS SENSITIVE AND WHAT WAS NOT, and generally why. A statistical analysis with respect to all 74 <data> is not feasible to explore within this paper. However, we consider these data types in our regression model.

>>>>

\subsection{Survey Questions}
In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]

@@

Friends 69.43\%, Work 74.12\%, Public 72.36\%, AppOnly 42.3\%

%SE: This doesn't add much, the numbers can be put in the text to save space.
%LL: Agreed.

%\begin{figure}
%	\centering
%	\includegraphics[width=0.5\textwidth]{recipient.png}
%	\caption{(This is a placeholder! TODO: generate a better plot for data recipient)}
%\end{figure}

@@

\subsubsection{Data Type}
Top and bottom absolute <data> rankings can be seen in Tables ~\ref{top10} and ~\ref{bottom10}. Irrespective with whom the data was shared or on what device, participants were most concerned about photos/videos, especially if they contain embarrassment, nudity, or financial information. Information which can be used to impersonate the user (i.e. username and password for websites) and invasions of privacy (photos of someone at home) were also considered to be sensitive data.

@@

A statistical analysis regarding the significance and confidence of <data> types with respect to all 74 was not performed due to the space constraints of the paper. We do consider all <data> in our regression model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
